---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# parsenet.pg

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of parsenet.pg is to ...

## Installation

You can install the development version from GitHub with:

``` r
install.packages("remotes")
remotes::install_github("celehs/parsenet.pg")
```

## Usage

### Build the database

```{r eval=FALSE}
library(parsenet.pg)
# required steps: df_edges and dict
data2db(data, "df_edges", db)
data2db(data, "dict", db)
# optional steps: some other data
data2db(data, "name of the data", db, title = "the title of the table", note = "description of the data")
```


### Set environment variables 

.Renviron is a user-controllable file that can be used to create environment variables. This is especially useful to avoid including credentials like API keys inside R scripts. 

#### Open .Renviron

```{r eval=FALSE}
# opens .Renviron
usethis::edit_r_environ()
```

#### Set environment variable

.Renviron is written in a key-value format, so environment variables are created in the format:

```
DB_HOST='host'
DB_PORT=port
DB_USER='username'
DB_PSWD='password'
```


### Run app

This is a basic example which shows you how to run the `parsenet.pg` app. Remember you need to get access to the data and save it to your local computer. In order to guarantee some dependencies are loaded, you must use `library(parsenet.pg)` beforehand, instead of directly running `parsenet.pg::run_app()`.


```{r eval=FALSE}
library(parsenet.pg)
run_app(db = "name of the database")
```



See the [getting started guide](https://celehs.github.io/parsenet.pg/articles/main.html)
to learn how to use parsenet.pg.

