---
title: "Data for network"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data for network}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Required data

## df_edges

A data.frame of "from-to-weight". demo:

| from        | to             | weight |
| ----------- | -------------- | ------ |
| PheCode:008 | PheCode:008.51 | 0.81   |
| PheCode:008 | RXNORM:123     | 0.62   |

- **from**: center nodes.
- **to**: collected nodes.
- **weight**: the weight of the collection. e.g. cosine similarity.

```{r eval=FALSE}
parsenet.pg::data2db(data, "df_edges", db)
```

## dict

Dictionary for nodes. demo:

| id             | type | label | term | semantic_type | group | group1 | group2 | category | level1 | level2 | level3 | level4 |
| -------------- | ------ | ------ | -------------------- | ------------------- | -------------- | ------- | ---------------- | -------------------- | ------------------- | ----------------- | ------ |
| C0000167       | NLP | 17 Ketosteroids | 17 Ketosteroids | Pharmacologic Substance       | Drug_NLP | CHEM   | Drug       | Chemicals & Drugs NLP |Pharmacologic Substance | 17 Ketosteroids | 
| PheCode:008    | Codified | intestinal infection | intestinal infection | infectious diseases | Disease_Codified | PheCode        | Disease | Disease Codified | intestinal infection |                     |                   |        |
| PheCode:008.5  | Codified | bacterial enteritis | bacterial enteritis  | infectious diseases | Disease_Codified | PheCode        | Disease | Disease Codified | intestinal infection | bacterial enteritis |                   |        |
| PheCode:008.51 | Codified | intestinal e.coli | intestinal e.coli    | infectious diseases | Disease_Codified | PheCode        | Disease | Disease Codified | intestinal infection | bacterial enteritis | intestinal e.coli |        |
| RXNORM:1000104 | Codified | incobotulinumtoxina | incobotulinumtoxina | hypoglycemic agents | Drug_Codified | RXNORM        | Drug | Drug Codified | glucagon-like peptide- | liraglutide | |        |
| CCS:177        | Codified | computerized axial tomography ct scan head | computerized axial tomography ct scan head | Miscellaneous diagnostic and therapeutic procedures | Procedure_Codified |  CCS        | Procedure | Procedure Codified | miscellaneous diagnostic and therapeutic procedures | computerized axial tomography ct scan | computerized axial tomography ct scan head |        |
| LOINC:10374-7  | Codified | helmet cells | helmet cells | Blood smear finding | Lab_Codified | LOINC        | Lab | Lab Codified | Hematology | Blood smear finding | Erythrocyte shape | helmet cells |

- **id**: The unique key. (e.g. PheCode:008)
- **type**: Different types will use nodes of different shapes in the network. (e.g. NLP / Codified)
- **label**: The string to be showed in the network. (e.g. intestinal infection)
- **term**: Description/Term/String of the ID. (e.g. intestinal infection)
- **semantic type**: semantic type/group. (e.g. infectious diseases)
- **group**: (e.g. "Procedure_NLP" "CHEM"  "Disease_NLP" "Drug_NLP"  "Lab_NLP" "PHYS"  "PHEN" "ACTI"  "Other_cui" for NLP nodes; "Procedure_Codified""Lab_Codified" "Disease_Codified" "Drug_Codified" for codified nodes)
- **group1**: (e.g. "CCS" "PheCode" "RXNORM" "Lab" for codified nodes; "PROC"   "CHEM"   "DISO"   "PHYS"   "PHEN"   "ACTI" for NLP nodes)
- **group2**: (e.g.  "Procedure" "Disease" "Drug" "Lab" "Ignore_cui")
- **category**: User specified group name. (e.g. "Procedure Codified"  "Disease Codified"    "Drug Codified"       "Lab Codified")
- **level1~4**:	The descriptions for hierarchical levels of `id` column. e.g. The hierarchy of PheCode:008.51:   
	* level1 is the top level (intestinal infection: PheCode:008)
	* level2 is the second level (bacterial enteritis: PheCode:008.5)
	* level3 is the bottom level itself (intestinal e.coli: PheCode:008.51)
	* level4 is NA

```{r eval=FALSE}
parsenet.pg::data2db(data, "dict", db)
```

# Optional data

**Note: **All the key colnumn should be names as id. 

## synonyms

| id  | synonyms |
| ---- | -------- |
|C0000167|17 Ketosteroids|
|C0000167|17-Ketosteroids|
|C0000167|17-Oxosteroids|
|C0000167|17 Oxosteroids|
|C0000167|17-Oxosteroid|
|C0000167|17 ketosteroid|
|C0000167|17-ketosteroid|

- **id**: center nodes' ID. (e.g. C3205666)
- **synonyms**: The synonyms.

```{r eval=FALSE}
parsenet.pg::data2db(data, "name of the data", db, title = "the title of the table", note = "description of the data")
```

## rollup

The first 2 column must be `id` and `cui`.

| id              | cui                             | term                   | semantic type                 | semantic group |
| --------------- | ------------------------------- | ---------------------- | ----------------------------- | -------------- |
| C3205666        | C0039226                        | Enteric-coated tablets | Biomedical or Dental Material | CHEM           |

- **id**: center nodes' ID. (e.g. C3205666)
- **cui**: The cui id rolluped to center nodes.
- **...**: optional columns.

## More data

The first column must be `id`.

| id           | LabChemTestName |
| ------------ | --------------- |
| LOINC:8122-4 | ABS CD3(096925) |

- **id**: center nodes' ID. (e.g. LOINC:8122-4)
- **...**: optional columns.

